### 2022-03-09 paper1.tex
Finish Background theory

\subsubsection{Google Trends}
This paper focuses on a validation of Google search trends \citep{googletrends}.
Google trends portray the search frequency for specific search terms across
designated media markets areas (DMAs), a nonoverlapping aggregation of U.S.
counties to 210 media markets based on similar population clusters \citep{dma_key}.
Raw data is on a scale from zero to one hundred, with one hundred being the maximum search
popularity out of all DMAs. When available, I use Google search topics to
measure trends as opposed to search terms. Search topics are a more robust
measurement than a single search term: topics are aggregations of the rates of
multiple, highly correlated search terms together into a cohesive topic. For
example, while 'Beyoncé', 'Beyonce' and 'beyonce knowles' are all separate
search terms, 'Beyoncé Knowles' encompasses all of these into a single search
topic. Google Search Trends are only available cross-sectionally (a single 
period across a geography) or as time-series (a single geo-location across
time). To remedy this and build a longitudinal dataset of each search topic 
to match the longitudinal validated measures, I follow the method proposed in \citet[p. 5]{park_etal}.
This method involves building a dataset of unscaled cross-sectional values,
selecting a DMA to use to establish the rescaling ratio (I use 'Los Angeles
CA'), and then finding the time-series values for the one DMA. To find the
rescaling ratio for each week in the time-series, you divide the time-series
value for each week by the cross-sectional value for each week, resulting in a
rescaling vector to be used for all weeks in the dataset across geographies. To
rescale each longitudinal value, multiply the respective week's rescaling ratio
by the cross-sectional value. To validate this method, I compared the rescaled
longitudinal data against multiple samples of time-series data. For a more
in-depth explanation of this procedure, see \citet[p. 5]{park_etal}. I interpolate 
missing datapoints in the longitudinal datasets using \texttt{zoo\:\:na\.approx\(\)} \citep{zoo}.

@@

I also use U.S. Covid-19 rates to validate health and disease related topics. I
retrieve U.S. county-level Covid-19 rates from \citet{covid_data}, who compile this
data based on reports from state and local health agencies. It is widely
acknowledged that there are biases in this data due to inconsistencies and
availability in testing as well as different community propensity to test
\citep{gu22, cdc20a} However, it is the best measure we have of actual case rates.
Case Rate is measured as number of cases per 100,000 population. Observations
vary from a minimum of zero to a maximum of 1460.46 for each Monday from January 27, 2020, through
December 27, 2021. There are 285,986 cases across 3,136 counties and 101
dates. Missing data were interpolated using \texttt{zoo\:\:na\.approx\(\)} \citep{zoo}.

I also use county-level suicide rates from the US Centers for Disease Control
and Prevention \citeyearpar{suic_data}. Data is grouped by year from 2010-2020. Raw death
rates are scaled by population size for each year and can be interpreted as the
death rate by suicide for every one thousand people. There are 34,683 total
cases, resulting from 10 observations of 3,147 counties. Missing data were interpolated using
\texttt{zoo\:\:na\.approx\(\)} \citep{zoo}. Measures range from 0.034 to 53.254.

>>>>

\subsubsection{Google Trends}
This paper focuses on a validation of Google search trends \citep{googletrends}.
Google trends portray the search frequency for specific search terms across
designated media markets areas (DMAs), a nonoverlapping aggregation of U.S.
counties to 210 media markets based on similar population clusters \citep{dma_key}.
Raw data is on a scale from zero to one hundred, with one hundred being the maximum search
popularity out of all DMAs. When available, I use Google search topics to
measure trends as opposed to search terms. Search topics are a more robust
measurement than a single search term: topics are aggregations of the rates of
multiple, highly correlated search terms together into a cohesive topic. For
example, while 'Beyoncé', 'Beyonce' and 'beyonce knowles' are all separate
search terms, 'Beyoncé Knowles' encompasses all of these into a single search
topic. Google Search Trends are only available cross-sectionally (a single 
period across a geography) or as time-series (a single geo-location across
time). To remedy this and build a longitudinal dataset of each search topic 
to match the longitudinal validated measures, I follow the method proposed in \citet[p. 5]{park_etal}.
This method involves building a dataset of unscaled cross-sectional values,
selecting a DMA to use to establish the rescaling ratio (I use 'Los Angeles
CA'), and then finding the time-series values for the one DMA. To find the
rescaling ratio for each week in the time-series, you divide the time-series
value for each week by the cross-sectional value for each week, resulting in a
rescaling vector to be used for all weeks in the dataset across geographies. To
rescale each longitudinal value, multiply the respective week's rescaling ratio
by the cross-sectional value. To validate this method, I compared the rescaled
longitudinal data against multiple samples of time-series data. For a more
in-depth explanation of this procedure, see \citet[p. 5]{park_etal}. I interpolate 
missing datapoints in the longitudinal datasets using \texttt{na.approx()} \citep{zoo}.

@@

I also use U.S. Covid-19 rates to validate health and disease related topics. I
retrieve U.S. county-level Covid-19 rates from \citet{covid_data}, who compile this
data based on reports from state and local health agencies. It is widely
acknowledged that there are biases in this data due to inconsistencies and
availability in testing as well as different community propensity to test
\citep{gu22, cdc20a} However, it is the best measure we have of actual case rates.
Case Rate is measured as number of cases per 100,000 population. Observations
vary from a minimum of zero to a maximum of 1460.46 for each Monday from January 27, 2020, through
December 27, 2021. There are 285,986 cases across 3,136 counties and 101
dates. Missing data were interpolated using \texttt{na.approx()} \citep{zoo}.

I also use county-level suicide rates from the US Centers for Disease Control
and Prevention \citeyearpar{suic_data}. Data is grouped by year from 2010-2020. Raw death
rates are scaled by population size for each year and can be interpreted as the
death rate by suicide for every one thousand people. There are 34,683 total
cases, resulting from 10 observations of 3,147 counties. Missing data were interpolated using
\texttt{na.approx()} \citep{zoo}. Measures range from 0.034 to 53.254.
